---
title: ""
format:
  html:
    theme: none
    css: styles.css
    toc: false
    smooth-scroll: true
    page-layout: full
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(dplyr)
library(purrr)
library(readr)
library(glue)
library(bib2df)
```

::: {.page-shell}

::: {.masthead}
::: {.masthead-main}

# Robby De Pauw

<p class="tagline">Senior Researcher · Visiting Professor · Biostatistics, Epidemiology, and Data-driven Health Research</p>

:::

::: {.masthead-side}
**Website**  
[robbydepauw.be](https://www.robbydepauw.be/)

**Email**  
[robby.depauw@sciensano.be](robby.depauw@sciensano.be)

**Location**  
Belgium
:::
:::

::: {.section-nav .no-print}
[About](#about)
[Experience](#experience)
[Education](#education)
[Publications](#publications)
[Shiny apps](#apps)
[Projects](#projects)
[PhD theses](#phd-theses)
[Contact](#contact)
:::

## About {#about}

I am a Senior Researcher at Sciensano and Visiting Professor at Ghent University. My work focuses on epidemiology, burden of disease, survey analysis, rehabilitation research, and the development of data-driven tools in R and Shiny.

I am particularly interested in translating complex health data into actionable insights for research, policy, and clinical practice.

## Experience {#experience}

### Senior Researcher — Sciensano

Public health monitoring, epidemiology, burden of disease, survey analyses, and dissemination tools.

### Visiting Professor — Ghent University

Teaching and supervision in biostatistics and epidemiology.

## Education {#education}

### PhD in Health Sciences

Ghent University

### MSc in Statistical Data Analysis

Ghent University

### MSc in Rehabilitation Sciences and Physiotherapy

Ghent University

## Publications {#publications}

```{r}
#| results: asis

bib_file <- "data/publications.bib"

if (file.exists(bib_file)) {

  bib <- bib2df::bib2df(bib_file)

  pubs <- bib |>
    transmute(
      year = suppressWarnings(as.integer(YEAR)),
      title = stringr::str_squish(gsub("[{}]", "", TITLE)),
      journal = stringr::str_squish(gsub("[{}]", "", dplyr::coalesce(JOURNAL, BOOKTITLE, ""))),
      authors = AUTHOR,
      doi = dplyr::coalesce(DOI, ""),
      url = dplyr::coalesce(URL, "")
    ) |>
    arrange(desc(year), title)

  make_pub <- function(year, title, journal, authors, doi, url) {

    authors_txt <- if (length(authors) == 0 || all(is.na(authors))) {
      ""
    } else {
      paste(unlist(authors), collapse = ", ")
    }

    link <- ""
    if (!is.na(url) && nzchar(url)) {
      link <- paste0('<a href="', url, '" target="_blank">Link</a>')
    } else if (!is.na(doi) && nzchar(doi)) {
      link <- paste0('<a href="https://doi.org/', doi, '" target="_blank">DOI</a>')
    }

    paste0(
      '<div class="pub-item">',
      '<div class="pub-year">', ifelse(is.na(year), "", year), '</div>',
      '<div class="pub-body">',
      '<p>', authors_txt, '</p>',
      '<p><strong>', title, '</strong></p>',
      '<p>', journal, if (nzchar(link)) paste0(' · ', link) else '', '</p>',
      '</div></div>'
    )
  }

  cat(paste(purrr::pmap_chr(pubs, make_pub), collapse = "\n"))

} else {

  cat('<p>Add your Zotero BibTeX export as <code>data/publications.bib</code>.</p>')

}
```

## Shiny apps {#apps}

```{r}
#| results: asis

apps_file <- "data/shiny_apps.csv"

if (file.exists(apps_file)) {

  apps <- readr::read_csv(apps_file, show_col_types = FALSE)

  required_cols <- c("name", "description", "url")
  if (all(required_cols %in% names(apps))) {

    if (!"github" %in% names(apps)) apps$github <- ""

    cards <- purrr::pmap_chr(
      apps,
      function(name, description, url, github = "", ...) {

        gh <- if (!is.na(github) && nzchar(github)) {
          paste0(' · <a href="', github, '" target="_blank">GitHub</a>')
        } else ""

        paste0(
          '<div class="card">',
          '<h3><a href="', url, '" target="_blank">', name, '</a></h3>',
          '<p>', description, '</p>',
          '<p><a href="', url, '" target="_blank">Open app</a>', gh, '</p>',
          '</div>'
        )
      }
    )

    cat('<div class="card-grid">')
    cat(paste(cards, collapse = "\n"))
    cat('</div>')

  } else {

    cat('<p>The file <code>data/shiny_apps.csv</code> must contain at least: <code>name</code>, <code>description</code>, <code>url</code>.</p>')

  }

} else {

  cat('<p>Add <code>data/shiny_apps.csv</code>.</p>')

}
```

## Projects {#projects}

```{r}
#| results: asis

projects_file <- "data/projects.csv"

if (file.exists(projects_file)) {

  projects <- readr::read_csv(projects_file, show_col_types = FALSE)

  required_cols <- c("name", "description")
  if (all(required_cols %in% names(projects))) {

    if (!"organisation" %in% names(projects)) projects$organisation <- ""
    if (!"link" %in% names(projects)) projects$link <- ""

    cards <- purrr::pmap_chr(
      projects,
      function(name, description, organisation = "", link = "", ...) {

        org_part <- if (!is.na(organisation) && nzchar(organisation)) {
          paste0('<p class="card-status">', organisation, '</p>')
        } else ""

        link_part <- if (!is.na(link) && nzchar(link)) {
          paste0('<p><a href="', link, '" target="_blank">More info</a></p>')
        } else ""

        paste0(
          '<div class="card">',
          '<h3>', name, '</h3>',
          org_part,
          '<p>', description, '</p>',
          link_part,
          '</div>'
        )
      }
    )

    cat('<div class="card-grid">')
    cat(paste(cards, collapse = "\n"))
    cat('</div>')

  } else {

    cat('<p>The file <code>data/projects.csv</code> must contain at least: <code>name</code>, <code>description</code>.</p>')

  }

} else {

  cat('<p>Add <code>data/projects.csv</code>.</p>')

}
```

## PhD theses {#phd-theses}

```{r}
#| results: asis

theses_file <- "data/phd_theses.csv"

if (file.exists(theses_file)) {

  theses <- readr::read_csv(theses_file, show_col_types = FALSE)

  required_cols <- c("title", "candidate", "institution", "period", "role")
  if (all(required_cols %in% names(theses))) {

    items <- purrr::pmap_chr(
      theses,
      function(title, candidate, institution, period, role, ...) {
        paste0(
          '<div class="thesis-item">',
          '<p><strong>', title, '</strong><br>',
          candidate, ' — ',
          institution, ' · ',
          period, ' · ',
          role,
          '</p>',
          '</div>'
        )
      }
    )

    cat(paste(items, collapse = "\n"))

  } else {

    cat('<p>The file <code>data/phd_theses.csv</code> must contain: <code>title</code>, <code>candidate</code>, <code>institution</code>, <code>period</code>, <code>role</code>.</p>')

  }

} else {

  cat('<p>Add <code>data/phd_theses.csv</code>.</p>')

}
```

## Contact {#contact}

**Email**  
[robby.depauw@sciensano.be](robby.depauw@sciensano.be)

**Website**  
[www.robbydepauw.be](https://www.robbydepauw.be/)
:::
