---
title: ""
---

```{r}
#| label: setup
library(dplyr)
library(readr)
library(purrr)
library(stringr)
library(bib2df)

# Output-format switch: HTML keeps the styled cards/grid; PDF gets clean markdown.
is_html <- knitr::is_html_output()

# Read a data file, returning NULL if it is absent.
rd <- function(f) if (file.exists(f)) readr::read_csv(f, show_col_types = FALSE) else NULL

# Generic row renderer. `html_row`/`pdf_row` are functions of a named list `r`
# (one row, every value coerced to character, NA -> ""). Using paste0 (not
# sprintf) so stray %-signs in the data are never treated as format specifiers.
emit <- function(df, html_row, pdf_row, sep = "\n") {
  if (is.null(df) || nrow(df) == 0) return(invisible())
  out <- character(nrow(df))
  for (i in seq_len(nrow(df))) {
    r <- lapply(df, function(col) { v <- col[[i]]; if (is.na(v)) "" else as.character(v) })
    out[i] <- if (is_html) html_row(r) else pdf_row(r)
  }
  cat(paste(out, collapse = sep))
  cat("\n")
}

# A "timeline" row: bold main line, a sub line, and a period shown on the left
# (HTML) or as a trailing detail (PDF).
tl_html <- function(main, sub, when)
  paste0('<div class="pub-item"><div class="pub-year">', when,
         '</div><div class="pub-body"><p><strong>', main, '</strong></p><p>',
         sub, '</p></div></div>')
tl_pdf <- function(main, sub, when)
  paste0('- **', main, '** — ', sub, if (nzchar(when)) paste0(' · ', when) else '')
```

::: {.page-shell}

::: {.masthead}

::: {.masthead-left}
```{r}
#| results: asis
photo <- "data/profile.jpg"
if (file.exists(photo)) {
  if (is_html) {
    cat(paste0('<div class="masthead-photo"><img class="profile-photo" src="',
               photo, '" alt="Robby De Pauw"></div>'))
  } else {
    cat(paste0(
      '```{=latex}\n',
      '\\begin{tikzpicture}\n',
      '\\clip[rounded corners=8pt] (0,0) rectangle (2.6,2.6);\n',
      '\\node[anchor=south west,inner sep=0] at (0,0) ',
      '{\\includegraphics[width=2.6cm,height=2.6cm]{', photo, '}};\n',
      '\\end{tikzpicture}\n', '```\n'))
  }
}
```

::: {.masthead-main}

# Robby De Pauw

[Senior Researcher · Visiting Professor · Biostatistics, Epidemiology & Data-driven Health Research]{.tagline}

Public-health researcher (PhD) combining health sciences with advanced methods in epidemiology, statistics and data science.

::: {.content-visible when-format="html"}
[⬇ Download PDF](Robby-De-Pauw-CV.pdf){.pdf-button}
:::

:::

:::

::: {.masthead-side}
**Email**  
[robby.depauw@sciensano.be](mailto:robby.depauw@sciensano.be)

**Website**  
[robbydepauw.be](https://www.robbydepauw.be/)

**ORCID**  
[0000-0002-4242-9062](https://orcid.org/0000-0002-4242-9062)

**Google Scholar**  
[Profile](https://scholar.google.com/citations?user=ZDPPxVkAAAAJ&hl=nl)

**Location**  
Belgium
:::
:::

::: {.content-visible when-format="html"}
::: {.section-nav .no-print}
[Profile](#profile)
[Experience](#experience)
[Education](#education)
[Funding](#funding)
[Projects](#projects)
[Publications](#publications)
[Teaching](#teaching)
[Supervision](#supervision)
[Talks](#talks)
[Service](#service)
[Contact](#contact)
:::
:::

## Profile {#profile}

Public-health researcher combining expertise in health sciences with advanced methodological skills in epidemiology, statistics and data science. My work bridges the individual (clinical) and population (epidemiological) levels, using linked patient and administrative data to identify gaps in care and applying advanced analytics to support causal, evidence-based decision-making. Core interests include burden-of-disease modelling, health inequalities, causal inference, biostatistics, and the translation of research into health policy. Experienced in leading multidisciplinary projects, securing competitive funding, and supervising students and doctoral researchers, with sustained work in both R and SAS.

## Experience {#experience}

```{r}
#| results: asis
d <- rd("data/appointments.csv")
emit(d,
  function(r) tl_html(r$role, r$institution, r$period),
  function(r) tl_pdf(r$role, r$institution, r$period))
```

## Education {#education}

```{r}
#| results: asis
d <- rd("data/education.csv")
emit(d,
  function(r) tl_html(r$qualification, r$institution, r$year),
  function(r) tl_pdf(r$qualification, r$institution, r$year))
```

*PhD dissertation:* “The motor brain in chronic neck pain — the association between motor impairment and brain differences in a population of chronic neck pain patients.” Supervisor: Prof. dr. Barbara Cagnie (Ghent University).

## Selected research achievements {#achievements}

**NEED project (Needs Examination, Evaluation and Dissemination).** Developed a methodological framework to systematically map unmet health-related needs, validated at EU level through a modified Delphi study. Secured BELSPO funding, designed the conceptual framework, and built the project dashboard and dataflow.

**High-impact fundamental research in *PAIN®*.** First-author graph-theoretical brain-network analysis in chronic neck pain, recognised as runner-up for best oral presentation at the European Congress of Manual Therapy.

**Large-scale population cohorts and data-linkage.** Designed complex population-level linkage projects including HELICON (COVID-19 health inequalities), the TeleHealth study, and a national long-COVID follow-up study.

**Recognised (inter)national analytical expertise.** Invited as an analytical expert on projects including a Scottish excess-weight modelling study (2003–2040), fungal diversity in bats, and validation of the SPIDER hypermobility questionnaire.

## Competitive research funding {#funding}

```{r}
#| results: asis
d <- rd("data/funding.csv")
emit(d,
  function(r) tl_html(r$project, paste0(r$funder, ' · ', r$amount), r$period),
  function(r) paste0('- **', r$project, '** — ', r$funder, ' · ', r$amount, ' · ', r$period))
```

Total competitive funding secured: approximately **€2,000,000**.

## Projects {#projects}

```{r}
#| results: asis
d <- rd("data/projects.csv")
if (is_html) cat('<div class="card-grid">\n')
emit(d,
  function(r) {
    org  <- if (nzchar(r$organisation)) paste0('<p class="card-status">', r$organisation, '</p>') else ''
    link <- if (nzchar(r$link)) paste0('<p><a href="', r$link, '" target="_blank">More info</a></p>') else ''
    paste0('<div class="card"><h3>', r$name, '</h3>', org, '<p>', r$description, '</p>', link, '</div>')
  },
  function(r) {
    org  <- if (nzchar(r$organisation)) paste0(' *(', r$organisation, ')*') else ''
    link <- if (nzchar(r$link)) paste0(' [More info](', r$link, ').') else ''
    paste0('**', r$name, '**', org, '. ', r$description, link, '\n')
  })
if (is_html) cat('</div>')
```

## Publications {#publications}

```{r}
#| results: asis

# Publications are driven by a Zotero BibTeX export (data/publications.bib).
# Export from Zotero to keep this section up to date — no code changes needed.
bib_file <- "data/publications.bib"

# safe column accessor: bib2df omits columns absent from every entry
col <- function(df, nm) if (nm %in% names(df)) df[[nm]] else rep(NA_character_, nrow(df))
# strip BibTeX braces, collapse whitespace, and turn "--" into a real en-dash
clean <- function(x) stringr::str_squish(gsub("--", "\u2013", gsub("[{}]", "", x)))

# Format one author list ("Family, Given" vectors) and bold Robby's own name.
fmt_authors <- function(a, bold) {
  if (length(a) == 0 || all(is.na(a))) return("")
  txt <- paste(unlist(a), collapse = ", ")
  gsub("De Pauw, Robby", if (bold) "<strong>De Pauw, Robby</strong>" else "**De Pauw, Robby**",
       txt, fixed = TRUE)
}

if (!file.exists(bib_file)) {
  cat('_Add your Zotero BibTeX export as `data/publications.bib`._')
} else {
  bib <- bib2df::bib2df(bib_file)
  pubs <- tibble::tibble(
    year    = suppressWarnings(as.integer(col(bib, "YEAR"))),
    title   = sub("\\.$", "", clean(col(bib, "TITLE"))),
    journal = clean(dplyr::coalesce(col(bib, "JOURNAL"), col(bib, "BOOKTITLE"), "")),
    volume  = clean(col(bib, "VOLUME")),
    number  = clean(col(bib, "NUMBER")),
    pages   = clean(col(bib, "PAGES")),
    doi     = dplyr::coalesce(col(bib, "DOI"), ""),
    url     = dplyr::coalesce(col(bib, "URL"), "")
  )
  pubs$authors <- col(bib, "AUTHOR")            # keep list-column intact
  pubs <- pubs[order(-pubs$year, pubs$title), ]

  # journal · volume(number) · pages  (each part only when present)
  venue_txt <- function(r) {
    v <- r$journal
    if (nzchar(r$volume)) v <- paste0(v, ', ', r$volume,
                                      if (nzchar(r$number)) paste0('(', r$number, ')') else '')
    if (nzchar(r$pages))  v <- paste0(v, ', ', r$pages)
    v
  }

  for (i in seq_len(nrow(pubs))) {
    r <- lapply(pubs, function(c) c[[i]])
    r <- lapply(r, function(v) if (length(v) == 1 && is.na(v)) "" else v)
    yr <- if (is.na(pubs$year[i])) "" else pubs$year[i]
    if (is_html) {
      a <- fmt_authors(r$authors, bold = TRUE)
      link <- if (nzchar(r$url)) paste0(' · <a href="', r$url, '" target="_blank">Link</a>')
              else if (nzchar(r$doi)) paste0(' · <a href="https://doi.org/', r$doi, '" target="_blank">DOI</a>')
              else ''
      cat(paste0('<div class="pub-item"><div class="pub-year">', yr,
                 '</div><div class="pub-body"><p class="pub-authors">', a,
                 '</p><p><strong>', r$title, '</strong></p><p class="pub-venue">',
                 venue_txt(r), link, '</p></div></div>\n'))
    } else {
      a <- fmt_authors(r$authors, bold = FALSE)
      link <- if (nzchar(r$url)) paste0(' · [Link](', r$url, ')')
              else if (nzchar(r$doi)) paste0(' · [DOI](https://doi.org/', r$doi, ')')
              else ''
      cat(paste0(a, ' (', yr, '). **', r$title, '.** *', venue_txt(r), '*', link, '\n\n'))
    }
  }
}
```

## Shiny apps {#apps}

```{r}
#| results: asis
apps <- rd("data/shiny_apps.csv")
if (is.null(apps) || nrow(apps) == 0) {
  cat(if (is_html)
        '<p class="muted">Selected interactive apps and dashboards will be listed here.</p>'
      else
        '_Selected interactive apps and dashboards will be listed here._')
} else {
  if (is_html) cat('<div class="card-grid">\n')
  emit(apps,
    function(r) {
      gh <- if (nzchar(r$github)) paste0(' · <a href="', r$github, '" target="_blank">GitHub</a>') else ''
      paste0('<div class="card"><h3><a href="', r$url, '" target="_blank">', r$name,
             '</a></h3><p>', r$description, '</p><p><a href="', r$url,
             '" target="_blank">Open app</a>', gh, '</p></div>')
    },
    function(r) {
      gh <- if (nzchar(r$github)) paste0(' · [GitHub](', r$github, ')') else ''
      paste0('**', r$name, '**. ', r$description, ' [Open app](', r$url, ')', gh, '\n')
    })
  if (is_html) cat('</div>')
}
```

## Teaching {#teaching}

```{r}
#| results: asis
d <- rd("data/teaching.csv")
emit(d,
  function(r) {
    ects <- if (nzchar(r$ects) && r$ects != "—") paste0(' · ', r$ects, ' ECTS') else ''
    tl_html(r$course, paste0(r$role, ' · ', r$institution, ects), '')
  },
  function(r) {
    ects <- if (nzchar(r$ects) && r$ects != "—") paste0(' · ', r$ects, ' ECTS') else ''
    paste0('- **', r$course, '** — ', r$role, ' · ', r$institution, ects)
  })
```

## Supervision {#supervision}

### Doctoral dissertations (as (co-)promotor or guidance-committee member)

```{r}
#| results: asis
d <- rd("data/phd_theses.csv")
emit(d,
  function(r) tl_html(r$title, paste0(r$candidate, ' · ', r$institution, ' · ', r$role), r$period),
  function(r) paste0('- **', r$title, '** — ', r$candidate, ' · ', r$institution,
                     ' · ', r$period, ' · ', r$role))
```

### Master’s theses (selected)

```{r}
#| results: asis
d <- rd("data/masters_theses.csv")
emit(d,
  function(r) {
    note <- if (nzchar(r$note)) paste0(' · <em>', r$note, '</em>') else ''
    cand <- if (nzchar(r$candidate)) paste0(r$candidate, ' · ') else ''
    tl_html(r$title, paste0(cand, r$institution, note), r$year)
  },
  function(r) {
    note <- if (nzchar(r$note)) paste0(' · *', r$note, '*') else ''
    cand <- if (nzchar(r$candidate)) paste0(r$candidate, ' · ') else ''
    paste0('- **', r$title, '** — ', cand, r$institution, ' · ', r$year, note)
  })
```

## Invited talks & oral presentations {#talks}

```{r}
#| results: asis
d <- rd("data/invited_talks.csv")
if (!is.null(d)) d <- dplyr::arrange(d, dplyr::desc(year))
emit(d,
  function(r) {
    loc <- if (nzchar(r$location)) paste0(', ', r$location) else ''
    inv <- if (identical(r$invited, "yes")) ' · invited' else ''
    tl_html(r$title, paste0(r$venue, loc, inv), r$year)
  },
  function(r) {
    loc <- if (nzchar(r$location)) paste0(', ', r$location) else ''
    inv <- if (identical(r$invited, "yes")) ' · invited' else ''
    paste0('- **', r$title, '** — ', r$venue, loc, inv, ' · ', r$year)
  })
```

## Prizes & awards {#awards}

```{r}
#| results: asis
d <- rd("data/awards.csv")
if (is_html) cat('<ul class="award-list">\n')
emit(d,
  function(r) paste0('<li>', r$award, '</li>'),
  function(r) paste0('- ', r$award))
if (is_html) cat('</ul>')
```

## Additional training & qualifications {#training}

```{r}
#| results: asis
d <- rd("data/training.csv")
emit(d,
  function(r) tl_html(r$item, r$institution, r$year),
  function(r) paste0('- **', r$item, '** — ', r$institution, ' · ', r$year))
```

## Academic service & engagement {#service}

- Head, Biostatistics Unit, Faculty of Medicine and Health Sciences, Ghent University (since 2025) — coordination and mission/vision development.
- Member, education committee of the MSc Statistical Data Analysis (2016–2019); scientific committee of the Department of Rehabilitation Sciences (since 2022); chair, REVAKI Alumni (since 2024).
- Member of two strategic working groups on the interfederal health objectives (FPS Public Health) and healthcare objectives (RIZIV–INAMI).
- Section editor, *Archives of Public Health* (2020–2025); guest editor, *Scientific Reports* (since 2024); Handling editor, *European journal of public health* (Since 2026)
- Peer reviewer for *The Lancet*, *Pain*, *BMC Public Health*, *European Journal of Public Health*, *BMJ Open*, and *PLOS ONE*.
- Member, WHO Health Information Network (European Region) and the European Burden of Disease Network (COST Action CA18218).
- Member, Sciensano AI-implementation steering group, Data Steward group, and R User Group.

## Societal impact & outreach {#impact}

- Translates research for policymakers and clinicians using the Data–Information–Knowledge–Wisdom (DIKW) structure within a Knowledge Translation framework, including a workshop at the European Public Health Conference on reaching policymakers with evidence.
- Media: featured in *Eos Wetenschap*; interviewed by VRT NWS, Studio Brussel and Nostalgie on disease-burden projections to 2040.
- Co-responsible for the Belgian Health Status Report ([gezondbelgie.be](https://www.gezondbelgie.be)).
- Lead researcher (Sciensano) for the NEED project and website ([unmet-needs.eu](https://unmet-needs.eu)); a project symposium was opened by the Minister of Public Health.

## Contact {#contact}

**Email**  
[robby.depauw@sciensano.be](mailto:robby.depauw@sciensano.be)

**Website**  
[www.robbydepauw.be](https://www.robbydepauw.be/)

**ORCID**  
[0000-0002-4242-9062](https://orcid.org/0000-0002-4242-9062)

**Google Scholar**  
[scholar.google.com](https://scholar.google.com/citations?user=ZDPPxVkAAAAJ&hl=nl)

:::
